\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[red]{casual}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}
\recomputelengths

\firstname{Firstname}
\familyname{Lastname}
\title{Padawan}
\address{Coruscant}{9999 The Republic}
\mobile{}
\email{}
\homepage{https://www.jannidar.com}
\social[twitter]{@jihillestad}
\social[github]{https://github.com/Jihillestad}
% \photo[64pt][0pt]{"./JannIdar.jpg"}

\begin{document}
\maketitle
\section{Skills}
\subsection{Key Skills}
\cvline{}{Relevant traits and what i'm good at. Make sure it's scoped for the job ad. Recruiters use AI tools.}

\subsection{Technical Skills}
\cventry{}{Functional}{}{}{}{Areas of knowledge I am proficient in.}

\cventry{}{Technology}{}{}{}{Azure, Microsoft 365, Microsoft Intune, SCCM, Windows client/server OS,
App-V, Linux, Catalog Services(Active Directory/Entra ID), VmWare, GIT/GitHub, Docker}

\cventry{}{Programming}{}{}{}{Powershell (expert), Terraform (basic level), JavaScript (basic level), React (basic level),
NextJS(basic level), Python (basic level),
HTML (basic level), CSS (basic level)}

\subsection{Certifications}
\cvline{2024}{\textbf{Microsoft Certified: Azure Administrator Associate}}
\cvline{2023}{\textbf{Microsoft 365 Certified: Fundamentals}}
\cvline{2019}{\textbf{Microsoft 365 Certified: Modern Desktop Administrator}}
\cvline{2015}{\textbf{ITIL Foundation}}

\section{Project Experience}
\cventry{2024}{Senior Consultant}{Medium sized gym company}{Oslo}{Norway}
{Solution Architect and technician. Migrating IMAP email accounts to the Customer's Microsoft 365 Tenant after a merger.}

\cventry{2023}{Senior Consultant - End-user computing}{A large municipality}{Oslo}{Norway}
{Solution architect and technician. Delivered improved and automated solutions managing BIOS and drivers for production
clients and for imaging new computers.}

\cventry{2021 - 2022}{Senior Application Packager}{Some Govt Office}{Oslo}{Norway}
{Examining, planning, packaging and deploying Critical Applications using SCCM, App-V
and Ivanti Workspace Control.}

\cventry{2020 - 2022}{Application Lifecycle Management}{Some Govt Office}{Oslo}{Norway}
{Application Lifecycle Management consultancy. Areas of responsibility: Examining, documenting, decommissioning, packaging and deployments.
Texhnololy used: SCCM and Confluence.}

\cventry{2017}{Windows 7 to Windows 10 migration, Law Firm 1}{Ex Employer}{Oslo}{Norway}
{Design and technical work. Repackaged applications and re-imaged computers to Windows 10.}

\cventry{2017}{Windows 7 to Windows 10 migration, Law Firm 2}{Ex Employer}{Oslo}{Norway}
{Design and technical work. Repackaged applications and re-imaged computers to Windows 10.}

\cventry{2017}{Windows 7 to Windows 10 migration, Law Firm 3}{Ex Employer}{Oslo}{Norway}
{Design and technical work. Repackaged applications and re-imaged computers to Windows 10.}

\cventry{2017}{Windows 7 to Windows 10 migration, Law Firm 3}{Ex Employer}{Oslo}{Norway}
{Design and technical work. Repackaged applications and re-imaged computers to Windows 10.}

\cventry{2010 - 2011}{Windows XP to Windows 7 migration, Some Govt Office}{Ex Employer}{Oslo}{Norway}
{Configured SCCM 2007 Operating System Deployment. Repackaged applications. Re-imaged computers to Windows 7.}

\section{Work Experience}
\cventry{2024 - current}{Senior Consultant}{Astrofarm AS}{Asker}{}
{Windows, Linux and Microsoft 365 operations. Made sure customer projects succeeded.}

\cventry{2019 - 2024}{Senior Solution Architect}{RedQ AS}{Oslo}{Norway}
{Consulting, solution design, pre-sales. Operational work in Microsoft 365, Intune and SCCM for hosting customers.}

\section{Education}
\cventry{2000 - 2003}{Jedi}{Jedi Temple}{Coruscant}{The Republic}
{Bachelor Thesis: Built a lightsaber.}

\section{Courses}
\cventry{2018}{Microsoft Intune Masterclass}{Glasspaper}{Oslo}{Norway}
{}

\cventry{2013}{System Center 2012 Configuration Manager - Masterclass}{Glasspaper}{Oslo}{Norway}
{}

\section{Languages}
\cvlanguage{Norwegian}{Native Language}{}
\cvlanguage{English}{Fluent spoken/written}{International work experience}

\section{References}
\begin{cvcolumns}
  \cvcolumn{}{\begin{itemize}
      \item Name, Title, Phone, Email 
      \item Name, Title, Phone, Email 
      \item Name, Title, Phone, Email 
      \item Name, Title, Phone, Email 
  \end{itemize}}
\end{cvcolumns}

\end{document}
